Master's Project Journal

### 2019-04-23 thesis/Introduction.tex
partial corrections

This thesis will put forward the \ac{FPGA} as a tool in the design of \ac{ADPLL} networks to bridge the gap between software simulations and implementation in custom silicon by providing a hardware-based simulation, modelling and validation platform. While an FPGA lacks the direct control over the schematic and layout that \iac{ASIC} provides, the hardware nature of this platform enables the analysis of system dynamics that are not easily modelled in simulation and the testing. \acp{ADPLL} are an entirely digital implementation of \iac{PLL}, advantageous as this allows for easier integration into the modern high transistor count \acl{IC} (\acs{IC}s) for which \ac{ADPLL} networks are a proposed clock distribution system.

The goal of this project is to design and implement an extensible platform that can be used by the research team in \ac{UCD} going forward as they seek to understand the behaviour of \ac{ADPLL} networks at a higher level and to serve as a hardware test-bed for proposed new architectures or system components. In order to accomplish this goal a number of potential \ac{ADPLL} architectures will be investigated, implemented and tested to ensure they are function correctly. Individual \acsp{ADPLL}, however, will not give sufficient insight into the behaviour of a network, so once the \ac{ADPLL} designs have been established, each will be implemented as part of a network of increasing sizes. Each contrasting design will be analysed based on the results of measurements and tests, and these results will be used to corroborate claims made regarding which \ac{FPGA} based \ac{ADPLL} design or \ac{ADPLL} network architecture is best suited for particular use cases.

The design of each block, or component part, used in the network will be discussed, starting with the reasons for their selection and an explanation of the design methodology, along with any major pitfalls encountered their creation. The impact on performance caused by modifying the design of these blocks will again be assessed on the basis of measurement results, before comparison is made to both theoretical expectations and their use case.

\Iac{FPGA} based test platform is ideal for those who wish to examine system dynamics without the time delays, financial burden or expertise required to develop a complete mixed-signal system on \iac{ASIC} but retain the ability to realistically simulate the behaviour of \iac{ADPLL} network. The result of this project is such a platform, designed to be extensible, with flexibility built into each component/module used.

>>>>

This thesis will propose the \ac{FPGA} as a tool in the design of \ac{ADPLL} networks, to bridge the gap between software simulations and implementation in custom silicon, by providing a hardware-based simulation, modelling and validation platform. While an FPGA lacks the direct control over the schematic and layout that \iac{ASIC} provides, the hardware nature of this platform enables the analysis of system dynamics that are not easily modelled in simulation and testing. \acp{ADPLL} are an entirely digital implementation of \iac{PLL}, advantageous as this allows for easier integration into the modern high transistor count \acl{IC} (\acs{IC}s) for which \ac{ADPLL} networks are a proposed clock distribution system.

The goal of this project is to design and implement an extensible platform that can be used by the research team in \ac{UCD} going forward, as they seek to understand the behaviour of \ac{ADPLL} networks at a higher level and to serve as a hardware test-bed for proposed new architectures or system components. In order to accomplish this goal, a number of potential \ac{ADPLL} architectures will be investigated, implemented and tested to ensure they function correctly. Individual \acsp{ADPLL}, however, will not give sufficient insight into the behaviour of a network, so once the \ac{ADPLL} designs have been established, each will be implemented as part of a network of increasing sizes. Each contrasting design will be analysed based on the results of measurements and tests, and these results will be used to corroborate claims made regarding which \ac{FPGA} based \ac{ADPLL} design or \ac{ADPLL} network architecture is best suited for particular use cases.

The design of each block, or component part, used in the network will be discussed, starting with the reasons for their selection and an explanation of the design methodology, along with any major pitfalls encountered in their creation. The impact on performance caused by modifications in the design of these blocks will again be assessed on the basis of measurement results, before comparison is made to both theoretical expectations and their use case.

\Iac{FPGA} based test platform is ideal for those who wish to examine system dynamics without the time delays, financial burden or expertise required to develop a complete mixed-signal system on \iac{ASIC}, yet simultaneously retaining the ability to realistically simulate the behaviour of \iac{ADPLL} network. The result of this project is such a platform, designed to be extensible, with flexibility built into each component/module used.

### 2019-04-23 thesis/LayAbstract.tex
partial corrections

\documentclass[11pt,english,british]{report}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3.5cm,rmargin=2.4cm}
\begin{document}
With the increasing proliferation of ``smart'' devices the need for low power yet high speed devices has never been greater. Each smart device contains a processor to control the device, each containing complex circuitry, requiring extremely exact synchronisation. The task of this synchronisation falls to the ``clock'' signal which must occur at the same instant in all areas of the processor. Conventional solutions to this problem cannot satisfy both power and speed requirements simultaneously, so designers have proposed the ADPLL Network which approaches the problem from the other side. Rather than generate the clock once and send it around the chip, which consumes a large amount of power, an ADPLL network divides the chip into a grid and generates many signals that each serve a local area, only requiring non time critical control signals to be sent over large distances.\\
The production of chips to test designs is both expensive and time consuming so designers must ensure that mistakes have not been made, accomplished by simulating the behaviour of the designs using complex behavioural and theoretical models. This thesis will discuss the use of Field Programmable Gate Arrays (FPGA) as a hardware testing, simulation and validation platform, to be used prior to test chip production, that is both cost and time effective. The hardware nature of an FPGA enables the analysis of behaviours that would not be possible in software, without the cost and time penalties of a custom chip. This is made possible by the ability to reconfigure the chip at will, albeit with comparatively lesser capabilities.\\
This thesis implements networks using three designs of ADPLL, each using a different architecture, and highlights the use cases to which each is best suited. The performance of each design is then analysed and this compared to the suggested use cases. Additionally the impact of more minor architectural modifications is tested and documented.
%what do I do?
\end{document}

>>>>

\documentclass[11pt,english,british]{report}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3.5cm,rmargin=2.4cm}
\begin{document}
With the increasing proliferation of ``smart'' devices, the need for lower power yet higher speed circuits has never been greater. Each smart device contains a processor to control the device, containing complex circuitry, requiring extremely exact synchronisation. The task of this synchronisation falls to the ``clock'' signal which must occur at the same instant in all areas of the processor. Conventional solutions to this problem cannot satisfy both power and speed requirements simultaneously, so designers have proposed the ADPLL Network takes a different approach to the problem. Rather than generate the clock once and send it around the chip, and action which consumes a large amount of power, an ADPLL network divides the chip into a grid and generates many signals that each serve a local area, thus only requiring non time-critical control signals to be sent over large distances.\\
The production of chips to test designs is both expensive and time consuming, so designers must ensure that mistakes have not been made. This is accomplished by simulating the behaviour of the designs, using complex behavioural and theoretical models. This thesis will discuss the use of Field Programmable Gate Arrays (FPGA) as a hardware testing, simulation and validation platform, to be used prior to test chip production, being both cost and time effective. The hardware nature of an FPGA enables the analysis of behaviours that would not be possible in software, without the cost and time penalties of a custom chip. This is made viable by the ability to reconfigure the chip at will, albeit with comparatively lesser capabilities.\\
This thesis implements networks using three designs of ADPLL, each using a different architecture, and highlights the use cases to which each is best suited. The performance of each design is then analysed and compared to the suggested use cases. Additionally the impact of more minor architectural modifications is tested and documented.
%what do I do?
\end{document}
